Learning to Infer Graphics Programs from Hand-Drawn Images

### 2017-05-19 paper.tex
added a single word

In the near future, we believe it will be possible to produce professional-looking figures just by drawing them and then letting an artificially-intelligent agent write the code.
More generally, we believe that the two-phase system we have proposed---parsing into execution traces, then searching for a low-cost symbolic program which generates those traces---may be a useful paradigm for domains in which agents must programmatically reason about noisy perceptual input.

>>>>

In the near future, we believe it will be possible to produce professional-looking figures just by drawing them and then letting an artificially-intelligent agent write the code.
More generally, we believe that the two-phase system we have proposed---parsing into execution traces, then searching for a low-cost symbolic program which generates those traces---may be a useful paradigm for other domains in which agents must programmatically reason about noisy perceptual input.
